Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-05-29 analysis/paper/London_HauloutBehavior.Rmd
reference pre-print with link
remove funding details form acknowledgements

This manuscript was developed as a reproducible research compendium. All data and
code are available on GitHub (https://github.com/noaa-afsc/berchukseals-haulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived
at the United States Animal Telemetry Network, archived at Movebank, or
associated with other published manuscripts (see supplemental 
material \@ref(tab:deploymentTable)). Collated and cleaned data products
needed to replicate the analysis along with the results of all model fits are 
also available and versioned as an R package on 
GitHub (https://github.com/noaa-afsc/berchuksealsHauloutFits) and archived at 
Zenodo.

@@

The findings and conclusions in the paper are those of the author(s) and do not
necessarily represent the views of the National Marine Fisheries Service, NOAA.
Any use of trade, product, or firm names does not imply an endorsement by the
U.S. Government. Funding for this study was provided by the U.S. National
Oceanic and Atmospheric Administration. Funding to ADF&G for tagging seals was provided by the Bureau of Ocean Energy
Management (No. M13PC0015 for work in Kotzebue, Alaska in 2009) and the Office
of Naval Research (No. N00014-16-1-3019).

>>>>

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print (https://doi.org/10.1101/2022.04.07.487572).
All data and code are available on GitHub
(https://github.com/noaa-afsc/berchukseals-haulout) and major versions archived
at Zenodo (https://doi.org/10.5281/zenodo.4638221). Original data sources for
telemetry are archived at the United States Animal Telemetry Network, archived
at Movebank, or associated with other published manuscripts (see supplemental
material \@ref(tab:deploymentTable)). Collated and cleaned data products needed
to replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(https://github.com/noaa-afsc/berchuksealsHauloutFits) and archived at Zenodo.

@@

The findings and conclusions in the paper are those of the author(s) and do not
necessarily represent the views of the National Marine Fisheries Service, NOAA.
Any use of trade, product, or firm names does not imply an endorsement by the
U.S. Government.
